Verifying Demonstrations

### 2017-09-28 properties.tex
Adds def of hardness of predicting future values

>>>>

There are two aspects of temporal eligibility.
The adversary can try to forge a witness for a future protest and the adversary 
can try to forge a witness for a past protest.

We first introduce something we call a \emph{time-authenticator tag}.
This is an unpredictable value \(\tau_t\) which is published at time \(t\).
The idea is that it is difficult to guess \(\tau_t\) for a given \(t\) in 
advance, i.e.\ the use of \(\tau_t\) must have happened after time \(t\) with 
high probability.

\begin{definition}[Predicting the future]
  Let \(T_t = (\tau_i)_{i=0}^{t}\) be the sequence of time-authenticator tags up 
  until time \(t\), where \(\tau_i\in \Z_{2^\lambda}\) for all \(i\).
  (\(\lambda\) is the security parameter.)
  Let \A be \iac{PPT} adversary.
  The challenger gives \(T_{t-1}\) to \A.
  \A is allowed to query an oracle \(O\) which returns whether a guess is 
  correct or not.
  If \(\A^O(T_{t-1},1^\lambda)\) outputs \(\tau\) such that \(\tau = \tau_t\) 
  the adversary wins.
\end{definition}

We can see that if \(\tau_t\) is chosen uniformly randomly then the adversary's 
chance of winning will be
\begin{equation}
  \label{SuccessOfPrediction}
  \Prob{%
    \A^O(T_{t-1}, \lambda) = \tau_t
  } = \frac{p(\lambda)}{2^\lambda}
\end{equation}
for some polynomial \(p(\cdot)\).
This will be negligible for sufficiently a large \(\lambda\).

\begin{definition}[Forging past witnesses]
  \dots
\end{definition}
